Manuscript for MADA Project

### 2023-04-24 code/analysis_code/statisticalanalysis.qmd
Updates

### Library
```{r}
library(tidymodels)
library(vip) #most important variables in LASSO Model
library(forcats)
library(tidyverse)
```

### creating a data frame that contains the variables that will be included in new linear regression mode. Just copying and pasting all of the totals generated from the `exploratoryanalysis.qmd` file
```{r}
#combined all relevant variables into 5 different data sets for each zip code. Got the black population totals for each zip code from  https://www.unitedstateszipcodes.org/31701/

Sum_by_month_31701 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          Total = c(7797, 7780, 7755, 7773, 7792, 7817),
                          Intervention = c(1, 1, 1, 1, 1, 1),
                          Male_Total = c(3371, 3358, 3368, 3379, 3387, 3397),
                          Female_Total = c(4426, 4422, 4387, 4394, 4405, 4420),
                          Age_05_09 = c(123, 126, 126, 127, 127, 128),
                          Age_10_17 = c(642, 635, 633, 637, 630, 629),
                          Age_18_44 = c(3310, 3316, 3313, 3323, 3325, 3331),
                          Age_45_64 = c(3229, 3244, 3239, 3259, 3264, 3258),
                          Age_65Plus = c(2576, 2570, 2569, 2574, 2568, 2572),
                          Pop = c(16475, 16475, 16475, 16475, 16475, 16475))

Sum_by_month_31705 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                                Total = c(10383, 10327, 10303, 10301, 10337, 10348),                                 Intervention = c(1, 1, 1, 1, 1, 1),
                          Male_Total = c(4394, 4397, 4399, 4391, 4403, 4399),
                          Female_Total = c(5989, 5930, 5904, 5910, 5934, 5949),
                          Age_05_09 = c(210, 211, 209, 201, 202, 202),
                          Age_10_17 = c(1159, 1171, 1169, 1163, 1168, 1167),
                          Age_18_44 = c(5201, 5215, 5239, 5263, 5278, 5281),
                          Age_45_64 = c(4380, 4381, 4366, 4364, 4367, 4367),
                          Age_65Plus = c(2983, 3000, 2997, 2997, 2994, 2989),
                          Pop = c(24779, 24779, 24779, 24779, 24779, 24779))

Sum_by_month_31707 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                                Total = c(9035, 8985, 8997, 9005, 9035, 9042),                                 Intervention = c(1, 1, 1, 1, 1, 1),
                          Male_Total = c(3698, 3674, 3678, 3680, 3684, 3681),
                          Female_Total = c(5337, 5311, 5319, 5325, 5351, 5361),
                          Age_05_09 = c(275, 277, 280, 282, 284, 283),
                          Age_10_17 = c(1109, 1120, 1125, 1134, 1136, 1142),
                          Age_18_44 = c(5903, 5931, 5943, 5947, 5960, 5958),  
                          Age_45_64 = c(5130, 5120, 5125, 5123, 5133, 5140),
                          Age_65Plus = c(4200, 4204, 4195, 4206, 4202, 4189),
                          Pop = c(13884, 13884, 13884, 13884, 13884, 13884))

Sum_by_month_30815 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          Total = c(8758, 8688, 8639, 8593, 8623, 8666),                                      Intervention = c(0, 0, 0, 0, 0, 0),
                          Male_Total = c(3526, 3514, 3503, 3484, 3489, 3498),
                          Female_Total = c(5232, 5174, 5136, 5109, 5134, 5168),
                          Age_05_09 = c(201, 213, 211, 215, 211, 211),
                          Age_10_17 = c(1116, 1113, 1115, 1118, 1115, 1114),
                          Age_18_44 = c(5001, 5009, 5020, 5026, 5025, 5032),
                          Age_45_64 = c(5026, 5017, 5020, 5009, 5013, 5020),
                          Age_65Plus = c(2816, 2825, 2827, 2814, 2828, 2832),
                          Pop = c(23481, 23481, 23481, 23481, 23481, 23481))

#um_by_month_30907 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          #Total = c(4956, 4917, 4888, 4851, 4866, 4894),                                      Zip = c(30907, 30907, 30907, 30907, 30907, 30907),
                          #Male_Total = c(1947, 1943, 1926, 1900, 1913, 1919),
                          #Female_Total = c(3009, 2974, 2962, 2951, 2953, 2975),
                          #Age_05_09 = c(244, 239, 241, 236, 240, 242),
                          #Age_10_17 = c(1344, 1358, 1357, 1341, 1343, 1335),
                          #Age_18_44 = c(9203, 9217, 9238, 9245, 9253, 9246),
                          #Age_45_64 = c(6740, 6700, 6667, 6626, 6617, 6624),
                          #Age_65Plus = c(6632, 6633, 6639, 6635, 6633, 6623),
                          #Pop = c(7744, 7744, 7744, 7744, 7744, 7744)) 
#the 30907 zip code population of residents that are black does not match the vaccination data. also this zip code does not have a majority of residents that are black like other other 4 zip codes so I am going to leave it out of the statistical analysis

#combining all of the zip codes into one data set except for the 30907 data 
combined = rbind(Sum_by_month_31701, Sum_by_month_31705, Sum_by_month_31707, Sum_by_month_30815)
```

### creating a vaccination rate variable as the outcome 
```{r}
combined$Vax_rate = (combined$Total / combined$Pop) * 100
```

### Creating a linear regression model 
```{r}
lm_model2 <- lm(Vax_rate ~ Intervention + Male_Total + Female_Total + Age_05_09 + Age_10_17 + Age_18_44 + Age_45_64 + Age_65Plus, data = combined)

summary(lm_model2)
```
The results indicate that Intervention is a significant predictor of Vax_rate, as indicated by its estimate of 16.23 and its marginally significant p-value of 0.067. This means that there is some evidence that the intervention has an effect on the vaccination rate

Male_Total is a significant negative predictor of Vax_rate, with a coefficient of -0.0133 and a significant p-value of 0.0054. This suggests that a higher male population is associated with a lower vaccination rate

Among the age groups, Age_65Plus is a significant positive predictor of Vax_rate, with a coefficient of 0.0114 and a marginally significant p-value of 0.055. This means that a higher proportion of the population in the age group 65 and above is associated with a higher vaccination rate

Overall, the model has a high adjusted R-squared value of 0.9995, indicating that the predictor variables account for a large proportion of the variation in Vax_rate. However, it is important to note that with such a high R-squared value, overfitting may be a concern, and it may be necessary to perform additional checks, such as cross-validation or regularization

### evaluating this model using RMSE 
```{r}
# Split the data into training and testing sets
train <- combined[1:15,]
test <- combined[16:24,]

# Train the linear regression model
model <- lm(Vax_rate ~ Intervention + Male_Total + Female_Total + 
             Age_05_09 + Age_10_17 + Age_18_44 + Age_45_64 + Age_65Plus, 
           data = train)

# Generate predictions for the test data
predictions <- predict(model, newdata = test)

# Calculate RMSE
rmse <- sqrt(mean((test$Vax_rate - predictions)^2))

rmse
```

### Train a LASSO model 
```{r}
Vax_split <- initial_split(combined, strata = Intervention)
Vax_train <- training(Vax_split)
Vax_test <- testing(Vax_split)
```

```{r}
Vax_rec <- recipe(Vax_rate ~ Intervention + Male_Total + Female_Total + 
             Age_05_09 + Age_10_17 + Age_18_44 + Age_45_64 + Age_65Plus, data = Vax_train) %>%
  step_zv(all_numeric(), -all_outcomes()) %>%
  step_normalize(all_numeric(), -all_outcomes()) #centering and scaling data 
```

```{r}
lasso_Vax <- linear_reg(penalty = 0.1, mixture = 1) %>%
  set_engine("glmnet")

wf <- workflow() %>%
  add_recipe(Vax_rec)

lasso_fit <- wf %>%
  add_model(lasso_Vax) %>%
  fit(data = Vax_train)

lasso_fit %>%
  pull_workflow_fit() %>%
  tidy()
```

### Tuning LASSO Parameters
```{r}
set.seed(1234)
Vax_boot <- bootstraps(Vax_train, strata = Intervention)

tune_spec <- linear_reg(penalty = tune(), mixture = 1) %>%
  set_engine("glmnet")

lambda_grid <- grid_regular(penalty(), levels = 50)
```

### Tune the grid
```{r}
set.seed(2020)
lasso_grid <- tune_grid(
  wf %>% add_model(tune_spec),
  resamples = Vax_boot,
  grid = lambda_grid
)
```

### Results 
```{r}
lasso_grid %>%
  collect_metrics()
```

### Visualizing the LASSO results 
```{r}
lasso_grid %>%
  collect_metrics()

lasso_grid_plot = lasso_grid %>%
  collect_metrics() %>%
  ggplot(aes(penalty, mean, color = .metric)) +
  geom_errorbar(aes(
    ymin = mean - std_err,
    ymax = mean + std_err
  ),
  alpha = 0.5
  ) +
  geom_line(size = 1.5) +
  facet_wrap(~.metric, scales = "free", nrow = 2) +
  scale_x_log10() +
  theme(legend.position = "none")

lasso_grid_plot
```

### Save plot
```{r}
#save figure
ggsave(filename = here("results","lasso_grid_plot.png"), plot=lasso_grid_plot)
```

### Lets pick the LASSO model with the lowest RMSE 
```{r}
lowest_rmse <- lasso_grid %>%
  select_best("rmse", maximize = FALSE)

final_lasso <- finalize_workflow(
  wf %>% add_model(tune_spec),
  lowest_rmse
)
```

### Final fit and viewing most important variables 
```{r}
final_lasso_plot = final_lasso %>%
  fit(Vax_train) %>%
  pull_workflow_fit() %>%
  vi(lambda = lowest_rmse$penalty) %>%
  mutate(
    Importance = abs(Importance),
    Variable = fct_reorder(Variable, Importance)
  ) %>%
  ggplot(aes(x = Importance, y = Variable, fill = Sign)) +
  geom_col() +
  scale_x_continuous(expand = c(0, 0)) +
  labs(y = NULL)
final_lasso_plot
```

### Looking at final fit 
```{r}
last_fit(
  final_lasso,
  Vax_split
) %>%
  collect_metrics()
```

### Save plot
```{r}
#save figure
ggsave(filename = here("results","final_lasso_plot.png"), plot=final_lasso_plot)
```

>>>>

### Library
```{r}
library(tidymodels)
library(vip) #most important variables in LASSO Model
library(forcats)
library(tidyverse)
library(Metrics) #RMSE
library(rsq) #rsqured 
library(yardstick)
library(MASS) #used for AIC forward selection 
library(glmnet) #for ridge regression 
```

```{r}

Sum_by_month_31701 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          TOTAL_VAX_RATE = c(7797/12768, 7780/12768, 7755/12897, 7773/12897, 7792/12897, 7817/12897),
                          Intervention = c(1, 1, 1, 1, 1, 1),
                          Male_VAX_RATE = c(3371/5981, 3358/5981, 3368/5981, 3379/5981, 3387/5981, 3397/5981),
                          Female_VAX_RATE = c(4426/6787, 4422/6787, 4387/6916, 4394/6916, 4405/6916, 4420/6916),
                          Age_05_09_VAX_RATE = c(123/1058, 126/1058, 126/1058, 127/1058, 127/1058, 128/1058),
                          Age_10_17_VAX_RATE = c(642/1560, 635/1560, 633/1560, 637/1560, 630/1560, 629/1560),
                          Age_18_44_VAX_RATE = c(3310/5054, 3316/5054, 3313/5054, 3323/5054, 3325/5054, 3331/5054),
                          Age_45_64_VAX_RATE = c(3229/4628, 3244/4628, 3239/4628, 3259/4628, 3264/4628, 3258/4628),
                          Age_65Plus_VAX_RATE = c(2576/2886, 2570/2886, 2569/2886, 2574/2886, 2568/2886, 2572/2886),
                          TOTAL_RATE_DIFF = c(0, 7780/12768 - 7797/12768, 7755/12897 - 7780/12768, 7773/12897 - 7755/12897, 7792/12897 - 7773/12897, 7817/12897 - 7792/12897), 
                          POP_n = c(12768, 12768, 12897, 12897, 12897, 12897),
                          Vac_n = c(7797, 7780, 7755, 7773, 7792, 7817))

Sum_by_month_31705 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                                TOTAL_VAX_RATE = c(10383/21603, 10327/21572, 10303/21722, 10301/21887, 10337/21887, 10348/21887),                                 Intervention = c(1, 1, 1, 1, 1, 1),
                          Male_VAX_RATE = c(4394/9885, 4397/9854, 4399/10004, 4391/10004, 4403/10004, 4399/10004),
                          Female_VAX_RATE = c(5989/11718, 5930/11718, 5904/11718, 5910/11883, 5934/11883, 5949/11883),
                          Age_05_09_VAX_RATE = c(210/1639, 211/1639, 209/1639, 201/1639, 202/1639, 202/1639),
                          Age_10_17_VAX_RATE = c(1159/3311, 1171/3311, 1169/3311, 1163/3311, 1168/3311, 1167/3311),
                          Age_18_44_VAX_RATE = c(5201/11978, 5215/11978, 5239/11978, 5263/11978, 5278/11978, 5281/11978),
                          Age_45_64_VAX_RATE = c(4380/6468, 4381/6468, 4366/6468, 4364/6468, 4367/6468, 4367/6468),
                          Age_65Plus_VAX_RATE = c(2983/3497, 3000/3497, 2997/3497, 2997/3497, 2994/3497, 2989/3497), 
                          TOTAL_RATE_DIFF = c(0, 10327/21572 - 10383/21603, 10303/21722 - 10327/21572, 10301/21887 - 10303/21722, 10337/21887 - 10301/21887, 10348/21887 - 10337/21887), 
                          POP_n = c(21603, 21572, 21722, 21887, 21887, 21887),
                          Vac_n = c(10383, 10327, 10303, 10301, 10337, 10348))

Sum_by_month_31707 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          TOTAL_VAX_RATE = c(9035/18045, 8985/18045, 8997/18045, 9005/18081, 9035/18081, 9042/18165),                                                       Intervention = c(1, 1, 1, 1, 1, 1),
                          Male_VAX_RATE = c(3698/8232, 3674/8232, 3678/8232, 3680/8232, 3684/8232, 3681/8232),
                          Female_VAX_RATE = c(5337/9813, 5311/9813, 5319/9813, 5325/9849, 5351/9849, 5361/9933),
                          Age_05_09_VAX_RATE = c(275/1583, 277/1702, 280/1702, 282/1702, 284/1702, 283/1702),
                          Age_10_17_VAX_RATE = c(1109/3001, 1120/3001, 1125/3001, 1134/3001, 1136/3001, 1142/3001),
                          Age_18_44_VAX_RATE = c(5903/11434, 5931/11434, 5943/11434, 5947/11434, 5960/11434, 5958/11434),
                          Age_45_64_VAX_RATE = c(5130/6051, 5120/6051, 5125/6051, 5123/6051, 5133/6051, 5140/6051),
                          Age_65Plus_VAX_RATE = c(4200/4259, 4204/4259, 4195/4259, 4206/4259, 4202/4259, 4189/4259), 
                          TOTAL_RATE_DIFF = c(0, 8985/18045 - 9035/18045, 8997/18045 - 8985/18045, 9005/18081 - 8997/18045, 9035/18081- 9005/18081, 9042/18165 - 9035/18081),                                                    
                          POP_n = c(18045, 18045, 18045, 18081, 18081, 18165),
                          Vac_n = c(9035, 8985, 8997, 9005, 9035, 9042))

Sum_by_month_30815 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          TOTAL_VAX_RATE = c(8758/19606, 8688/19736, 8639/19736, 8593/19736, 8623/19736, 8666/19736),                                                       Intervention = c(0, 0, 0, 0, 0, 0),
                          Male_VAX_RATE = c(3526/9066, 3514/9196, 3503/9196, 3484/9196, 3489/9196, 3498/9196),
                          Female_VAX_RATE = c(5232/10540, 5174/10540, 5136/10540, 5109/10540, 5134/10540, 5168/10540),
                          Age_05_09_VAX_RATE = c(201/2388, 213/2388, 211/2480, 215/2480, 211/2480, 211/2480),
                          Age_10_17_VAX_RATE = c(1116/3604, 1113/3604, 1115/3604, 1118/3604, 1115/3604, 1114/3604),
                          Age_18_44_VAX_RATE = c(5001/13358, 5009/13358, 5020/13358, 5026/13358, 5025/13358, 5032/13358),
                          Age_45_64_VAX_RATE = c(5026/8431, 5017/8431, 5020/8431, 5009/8431, 5013/8431, 5020/8431),
                          Age_65Plus_VAX_RATE = c(2816/3590, 2825/3590, 2827/3590, 2814/3590, 2828/3590, 2832/3590),
                          TOTAL_RATE_DIFF = c(0, 8688/19736 - 8758/19606, 8639/19736 - 8688/19736, 8593/19736 - 8639/19736, 8623/19736- 8593/19736, 8666/19736 - 8623/19736),
                          POP_n = c(19606, 19736, 19736, 19736, 19736, 19736),
                          Vac_n = c(8758, 8688, 8639, 8593, 8623, 8666))

Sum_by_month_30907 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          TOTAL_VAX_RATE = c(4956/9122, 4917/9189, 4888/9189, 4851/9189, 4866/9189, 4894/9189),                                                                      Intervention = c(0, 0, 0, 0, 0, 0),
                          Male_VAX_RATE = c(1947/4289, 1943/4289, 1926/4289, 1900/4289, 1913/4289, 1919/4289),
                          Female_VAX_RATE = c(3009/4833, 2974/4900, 2962/4900, 2951/4900, 2953/4900, 2975/4900),
                          Age_05_09_VAX_RATE = c(244/2174, 239/2174, 241/2174, 236/2174, 240/2174, 242/2174),
                          Age_10_17_VAX_RATE = c(1344/4070, 1358/4070, 1357/4070, 1341/4070, 1343/4070, 1335/4070),
                          Age_18_44_VAX_RATE = c(9203/14571, 9217/14571, 9238/14571, 9245/14571, 9253/14571, 9246/14571),
                          Age_45_64_VAX_RATE = c(6740/10362, 6700/10362, 6667/10362, 6626/10362, 6617/10362, 6624/10362),
                          Age_65Plus_VAX_RATE = c(6632/6995, 6633/6995, 6639/6995, 6635/6995, 6633/6995, 6623/6995), 
                          TOTAL_RATE_DIFF = c(0, 4917/9189 - 4956/9122, 4888/9189 - 4917/9189, 4851/9189 - 4888/9189, 4866/9189 - 4851/9189, 4894/9189 - 4866/9189),
                          POP_n = c(9122, 9189, 9189, 9189, 9189, 9189),
                          Vac_n = c(4956, 4917, 4888, 4851, 4866, 4894))

#combining all of the zip codes into one data 
combined = rbind(Sum_by_month_31701, Sum_by_month_31705, Sum_by_month_31707, Sum_by_month_30815,Sum_by_month_30907)

#multiply all rates by 100 
combined <- combined %>% 
  mutate(TOTAL_VAX_RATE = TOTAL_VAX_RATE * 100,
         Male_VAX_RATE = Male_VAX_RATE * 100,
         Female_VAX_RATE = Female_VAX_RATE * 100,
         Age_05_09_VAX_RATE = Age_05_09_VAX_RATE * 100,
         Age_10_17_VAX_RATE = Age_10_17_VAX_RATE * 100,
         Age_18_44_VAX_RATE = Age_18_44_VAX_RATE * 100,
         Age_45_64_VAX_RATE = Age_45_64_VAX_RATE * 100,
         Age_65Plus_VAX_RATE = Age_65Plus_VAX_RATE * 100,
         TOTAL_RATE_DIFF = TOTAL_RATE_DIFF * 100)

```

### Data splitting

```{r}
data_split = initial_split(combined, prop = 7/10, strata = TOTAL_RATE_DIFF)
```

### Splitting the data between training and testing

```{r}
train_data = training(data_split)
test_data  = testing(data_split)
```

### Doing 5-fold cross validation with 5 repeats and body temperature as the strata

```{r}
CV_fold = vfold_cv(train_data, v = 2, repeats = 5, strata = TOTAL_RATE_DIFF) 
```

### Creating a recipe and applying to the training data

```{r}
recipe <- recipe(TOTAL_RATE_DIFF ~ TOTAL_VAX_RATE + Intervention + Male_VAX_RATE + Female_VAX_RATE + Age_05_09_VAX_RATE + Age_10_17_VAX_RATE + Age_18_44_VAX_RATE + Age_45_64_VAX_RATE + Age_65Plus_VAX_RATE + Date + POP_n + Vac_n, data = train_data) %>%
  step_dummy(all_nominal(), one_hot = TRUE) #In this code, we create a recipe using step_dummy to preprocess the data and convert the categorical predictors into numeric predictors
```

## Creating a mean null model and evaluating the model for both the training data and test data

```{r}
mean_null_model <- function(combined) {
  outcome <- mean(combined$TOTAL_RATE_DIFF)
  prediction <- rep(outcome, nrow(combined))
  return(prediction)}

#using model to make predictions based on the training data and test data
train_pred <- mean_null_model(train_data)
test_pred <- mean_null_model(test_data)

#calculating rmse for the model fit to training data 
train_rmse <- rmse(train_data$TOTAL_RATE_DIFF, train_pred)
test_rmse <- rmse(test_data$TOTAL_RATE_DIFF, test_pred)

#taking a look at the rmse for both training and test data
train_rmse
test_rmse
```

## Creating a tree model and evaluating the model 
### Tuning Hyperparameters

```{r}
#tuning: the process of estimating the best values for these values by training many models on resampled data sets and exploring how well all these models perform
tune_spec <- 
  decision_tree(
    cost_complexity = tune(),
    tree_depth = tune()
  ) %>% 
  set_engine("rpart") %>% 
  set_mode("regression")
```

### Creating a grid of values

```{r}
tree_grid <- grid_regular(cost_complexity(),
                          tree_depth(),
                          levels = 5)
```

### Setting up a tree workflow

```{r}
tree_wf <- workflow() %>%
  add_model(tune_spec) %>%
  add_recipe(recipe)

#getting turning results 
tree_res <- 
  tree_wf %>% 
  tune_grid(
    resamples = CV_fold,
    grid = tree_grid
    )

tree_res %>%  collect_metrics()
```

### Plotting results of the tree model

```{r}
tree_res %>%
  collect_metrics() %>%
  mutate(tree_depth = factor(tree_depth)) %>%
  ggplot(aes(cost_complexity, mean, color = tree_depth)) +
  geom_line(linewidth = 1.5, alpha = 0.6) +
  geom_point(size = 2) +
  facet_wrap(~ .metric, scales = "free", nrow = 2) +
  scale_x_log10(labels = scales::label_number()) +
  scale_color_viridis_d(option = "plasma", begin = .9, end = 0)
```

### Taking a look at the best tree models based on the R\^2 values

```{r}
tree_res %>%
  show_best("rmse")

best_tree = tree_res %>%
  select_best("rmse")

best_tree
```

### Finalizing model

```{r}
final_wf <- 
  tree_wf %>% 
  finalize_workflow(best_tree)

final_wf
```

### Evaluate the final fit for the tree model

```{r}
final_fit <- 
  final_wf %>%
  last_fit(data_split)

final_fit_metrics <- final_fit %>%
  collect_metrics()
#final fit metrics
final_fit_metrics

#creating a tibble for predicted values of model
predictions = final_fit  %>%
  collect_predictions

#plotting model predictions vs actual outcome 
plot1 = final_fit %>%
  collect_predictions  %>%
    ggplot(aes(x = .pred, y = TOTAL_RATE_DIFF)) +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Predicted Probability") +
  ylab("Actual Class") +
  ggtitle("Predicted Values vs Actual Outcome Values")
plot1

#plotting the residuals 
residuals = predictions$TOTAL_RATE_DIFF - predictions$.pred

#creating a residual data frame 
residuals_df = data.frame(TOTAL_RATE_DIFF = predictions$TOTAL_RATE_DIFF, Predictions = predictions$.pred, Residuals = residuals)

# Create a scatter plot with ggplot for residuals 
ggplot(residuals_df, aes(x = Predictions , y = Residuals)) +
  geom_point() +
  xlab("Predicted values") +
  ylab("Residuals") +
  ggtitle("Residual Plot")

```

## Fitting for LASSO model

### Building a model

```{r}
lm_mod =
  linear_reg(penalty = tune(), mixture =1) %>%
  set_engine("glmnet")
```

### Creating a workflow

```{r}
lm_workflow =
  workflow() %>%
  add_model(lm_mod)  %>%
  add_recipe(recipe)
```

### Creating a grid for tuning

```{r}
lm_reg_grid <- tibble(penalty = 10^seq(-4, -1, length.out = 30))

# lowest penalty values
lm_reg_grid %>% top_n(-5)

# highest penalty values 
lm_reg_grid %>% top_n(5)

```

### Train and tune the model

```{r}
lasso_res <- lm_workflow %>%
  tune_grid(resamples = CV_fold, grid = lm_reg_grid)
```

### Collect metrics and picking the best model

```{r}
lasso_res %>% show_best("rmse")

best_lasso = lasso_res %>%
  select_best("rmse")
best_lasso
```

### Finalizing Lasso model

```{r}
final_lasso_wf <- 
  lm_workflow %>% 
  finalize_workflow(best_lasso)

final_lasso_wf
```

### 2023-04-24 products/Manuscript.qmd
Updates

# Summary

Back in March 2020, COVID-19 began to disproportionately impact the citizens of the United States. Among African Americans sub-population in rural South Georgia, there was a call to increase access to health services, promote health literacy as it relates to COVID-19 and decrease vaccine hesitancy. One such program includes the partnership between the City of Albany, GA and Albany State University to reduce COVID-19 vaccine hesitancy in Albany through a $3.9 million grant from Health and Human Services and the Office of Minority Health.

This study aims to conduct a secondary analysis of residents in Albany, GA that have received at least one dose of the COVID-19 vaccine and live in the one of the three zip codes 31701, 31705 and 31707.

@@

## General Background

@@

My goal is to compare monthly trends of vaccinations and examine whether there is an increase in vaccinations among African American residents during the time of the health literacy program, which is from September through April.

@@

In preparation for analysis, the raw data was first sub-setted by  Dougherty County, the county in which Albany, Georgia lies. This allowed me to work only with census tracts from Dougherty county. I then summed the data by demographic to get demographic totals.

>>>>

# Summary
This study aims to conduct a secondary analysis of residents of the black community in Albany, GA that have received at least one dose of the COVID-19 vaccine from September 2022 through February 2023 and live in the one of the three zip codes 31701, 31705 and 31707. The outcome of interest is the difference in vaccination rates by month from September through February. The predictor of interest is the presence of a COVID-19 Vaccine Hesitancy Program Intervention.

@@

## General Background
Back in March 2020, COVID-19 greatly impacted the citizens of the Albany, GA. Early on in the COVID-19 pandemic Albany, GA was ranked the "forth-worst" city hit by COVID-19 in the United States [@grahamrapierHowSmallGeorgia2020]. According to U.S Census Bureau, 74.5% of the total population of the City of Albany is made up by residents that are black. In a study that examined the health outcomes of residents who tested positive for COVID-19 in Albany, GA it was found that 83.3% of 710 patients that were hospitalized for COVID-19 were black[@]. Although there was no differences in hospital mortality found between residents that were black compared to residents that were not black but there was a much higher percentage of hospitalizations due to COVID-19 for residents who were black.

In July 2022, Albany was awarded a 3.9 million dollar grant from the Health and Human Services and the Office of Minority Health in an effort to fund COVID-19 vaccine hesitancy and health literacy programs[]. The Economic Evaluation Research Group (EERG) out of the University of Georgia College of Public Health Department of Health Policy and Management led by Dr. Janani Rajbhandari-Thapa is currently conducting an evaluation on the federally funded programs.

This study serves an extension of the evaluation being conducted by EERG through examining the vaccination rates of the zip codes where vaccine hesitancy programs are being conducted.

@@

My goal is to compare monthly trends of vaccinations and examine whether there is a noticable change in vaccination rates among residents who are black during the time of the health literacy programs, which is from September through February.

@@

In preparation for analysis, the raw data was first subsetted by Dougherty County, the county in which Albany, Georgia lies. This allowed me to work only with census tracts from Dougherty county. I then stratified the data by black residents. Of black residents, I summed the vaccination totals and populations by gender, age for each intervention zip code (31701, 31705 and 31707) and the two control zip codes.
